%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size and paper size

%\usepackage{fontspec} % For loading fonts
%\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin-SmallCaps]{Fontin} % Main document font

%\usepackage{xunicode,xltxtra,url} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

%\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}
\usepackage[margin=0.7in]{geometry}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage[version=4]{mhchem}
\usepackage{bibentry}
\usepackage{tabularx}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}  % right multiline alignment
\usepackage{booktabs}% http://ctan.org/pkg/booktabs
\newcommand{\bulletitem}{~~\llap{\textbullet}~~}
\newcommand{\tabitem}{~~\llap{}~~}
\usepackage{enumitem}
\setlist{nosep,after=\strut}
\usepackage{amsmath,amssymb}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{-3pt}{-3pt} % Spacing around sections

\begin{document}

\setlength{\parskip}{\baselineskip}%
\pagestyle{empty} % Removes page numbering

%\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{center}
	{\huge{\textsc{Michinari Sakai}}}\\% Your name
	\noindent\begin{tabular}{r @{$\quad\bullet\quad$} l}
		\href{mailto:michsakai@ucla.edu}{michsakai@ucla.edu} & 808-206-4357
	\end{tabular}
\end{center}

%\section{Personal Data}
%
%\begin{center}
%\noindent\begin{tabular}{rl}
%%\textsc{Place and Date of Birth:} & Los Angeles, USA  | 16 October 1980\\
%%\textsc{Place of Birth:} & Los Angeles, USA\\
%%\textsc{Address:} & 475 Portola Plaza \#5-123B, Los Angeles, CA 90095, USA\\
%%\textsc{Phone:} & +1-808-206-4357\\
%%\textsc{email:} & \href{mailto:michsakai@ucla.edu}{michsakai@ucla.edu}
%\end{tabular}
%\end{center}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

%\noindent\begin{tabular}{rp{10.3cm}}	
	\noindent\begin{tabularx}{\linewidth}{@{}lR@{}}	
	%\textsc{PhD, Experimental Neutrino Physics} & \textsc{2016}\\
		\textsc{PhD, Experimental Particle/Neutrino Physics} & \textsc{2016}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\begin{itemize}
			\item[] GPA: 4.0/4.0, University of Hawaii at Manoa
			\item[] Dissertation: High Energy Neutrino Analysis at KamLAND and Application to Dark Matter Search
		\end{itemize}
	\end{minipage}}\\
	%\small GPA: 3.97/4.00 &\\
	%\small Advisor: Prof. John G. \textsc{Learned} & \\

%------------------------------------------------

	\textsc{Graduate Program in Mathematics} & \textsc{2006}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\begin{itemize}
			\item[] GPA: 4.5/4.5, Sun Moon University, S.~Korea
		\end{itemize}
	\end{minipage}}\\
	%\small GPA: 4.50/4.50 &\\
	%& \small Advisor: Prof. Doe-Wan \textsc{Kim}\\

%------------------------------------------------

	\textsc{Double BS, Physics and Mathematics} & \textsc{2005}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\begin{itemize}
			\item[] GPA: 4.3/4.5, Sun Moon University, S.~Korea
			\item[] President's Award 2005, Award for Outstanding Academic Achievement -- Samsung Corp.
		\end{itemize}
	\end{minipage}}\\
	%\small Summa Cum Laude, GPA: 4.33/4.50&\\
	%& \small Advisor: Prof. Ki-Won \textsc{Kim}\\

%------------------------------------------------

\end{tabularx}

%----------------------------------------------------------------------------------------
%	SCHOLARSHIPS AND AWARDS
%----------------------------------------------------------------------------------------

%\section{Scholarships and Awards}
%
%\noindent\begin{tabular}{rl}
%	2004 & Award for Outstanding Academic Achievement, Samsung Corp.\\
%	2001 - 2004 & Undergraduate Achievement Scholarships, Sun Moon
%	Univ.\\
%	2001 & Ae-Guk Freshman Scholarship, Sun Moon Univ.\\
%\end{tabular}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE 
%----------------------------------------------------------------------------------------

\section{Leadership and Research}

%\noindent\begin{tabular}{r|p{10.4cm}}
\noindent\begin{tabularx}{\linewidth}{@{}lR@{}}
	\textsc{KamLAND (Kamioka Liquid Scintillator Antineutrino Detector)} & \textsc{2009 - 2016}\\
	%Research Assistant, University of Hawaii & \textsc{Aug. 2009 - Apr. 2016}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\textit{Research Assistant, University of Hawaii at Manoa}
		\begin{itemize}
			\item Spearheaded development of novel directional neutrino
				detection technique in scintillator and demonstrated with data
				that this can be used to conduct dark matter searches in
				scintillator, first ever physics application of neutrino
				directionaly in scintillator
			\item Led unprecedented particle ID capability studies in
				scintillator using track profile reconstruction techniques
				using never before observed T2K events spilling into KamLAND
			\item Was solely responsible for high energy
				($\gtrsim$\SI{1}{\giga\electronvolt}) energy calibration using
				cosmic ray muons and applying this to neutrino analysis for
				the first time
		\end{itemize}
	\end{minipage}}\\
	%\textbf{CUORE (Cryogenic Underground Observatory for Rare Events)} & \textsc{Apr. 2016 -} \textit{Current}\\
	\textsc{CUORE (Cryogenic Underground Observatory for Rare Events)} & \textsc{Apr. 2016 -} \textit{Current}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\textit{Post-doctoral Scholar, University of California, Los Angeles (UCLA)}
		\begin{itemize}
			\item Spearheading development of precision alpha background
				modeling in collaboration with a graduate student with goal for
				further background reduction to cover inverted neutrino mass
				hierarchy for $0\nu\beta\beta$ decay
			\item Mentored and worked with 2 undergraduate students for
				investigation of shielding structures to mitigate $\gamma$ and
				beta backgrounds for next generation $0\nu\beta\beta$ decay
				searches requiring ultra-low background levels
			%\item Implemented bolometer thermal model to create mock data for
			%	first data taking
		\end{itemize}
	\end{minipage}}\\
	\textsc{Mini-TimeCube (Portable Neutrino Detector)} & \textsc{2009 - 2016}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\textit{Research Assistant, University of Hawaii at Manoa}
		\begin{itemize}
			\item Led development of Geant4 detector simulation and
				mentored 3 undergraduate students to contribute to the overall
				detector design
			%\item Led critical role in directional neutrino/neutron
			%	reconstruction algorithm
			\item Was responsible for background studies associated with long
				lived cosmogenic isotopes \ce{8}He/\ce{9}Li, to quantitatively
				determine effect on detector live time
			%\item Spearheaded trade studies for \ce{Li}/\ce{B} neutron capture
			%	dopants in scintillator
		\end{itemize}
	\end{minipage}}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\section{Teaching Experience}

\noindent\begin{tabularx}{\linewidth}{@{}lR@{}}
%\textsc{Aug. 2007 - May. 2009} & Teaching Assistant, University of Hawaii at Manoa\\
	\textsc{Mentor}, \textit{UCLA} & \textsc{2016 -} \textit{Current}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\begin{itemize}
			\item Taught weekly Geant4 simulation tutorials to \num{3}
				PhD students and \num{3} undergraduate students for 1 semester,
				students are now able to take on simulation tasks and
				collaborate in the group
			\item Led weekly Physics paper discussion groups for \num{3} PhD
				students, and promoted team work to increase dialogue and
				productivity within team
		\end{itemize}
	\end{minipage}}\\
	\textsc{Teaching Assistant}, \textit{University of Hawaii at Manoa} & \textsc{2007 - 2009}\\
	\multicolumn{2}{@{}l@{}}{\begin{minipage}[t]{\linewidth}
		\begin{itemize}
			\item Planned classwork and taught 2 weekly undergraduate Physics
				Laboratory classes of over \num{20} students each for 3
				semesters, received ``excellent'' reviews
			\item Mentored undergraduate students in undergraduate Physics
				classwork for 2 hours each week for 3 semesters, got students
				repeatedly seeking my particular tutoring
		\end{itemize}
	\end{minipage}}\\

%------------------------------------------------

%%\textsc{Jan. 2003 - Mar. 2006} & Interpreter and Teacher\\
%	\textbf{Interpreter and Teacher} & \textsc{2003 - 2006}\\
%	\multicolumn{2}{X}{Part time English lecturer for Korean undergraduate students.}\\
%	\multicolumn{2}{X}{Part time contributing reporter and translator for campus magazine.}\\
%	\multicolumn{2}{X}{Spontaneous trilingual interpreter for W-CARP International Education Conference.}\\
%	\multicolumn{2}{X}{Part time translator for magazine Today's World.}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS 
%----------------------------------------------------------------------------------------

\section{Skills}

\noindent\begin{tabularx}{\linewidth}{@{}rl}
	Human Languages: & English (native), Japanese/Korean (trilingual proficiency)\\
	Programming Languages: & Proficient in C, C++, Python, Fortran, Mathematica, Bash\\
	Software/Tools: & \textsc{ROOT}, \textsc{Geant4}, \textsc{Pads}, \textsc{AutoCAD}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

%\section{Languages}
%
%\noindent\begin{tabular}{rl}
%	\textsc{English}, \textsc{Japanese}, \textsc{Korean}\\
%\end{tabular}
%
%\newpage

%----------------------------------------------------------------------------------------
%	POSTERS AND TALKS
%----------------------------------------------------------------------------------------

\clearpage
\section{Invited Talks and Presentations}

\noindent\begin{tabularx}{\linewidth}{@{{}\textbullet\enskip}X@{\quad}r@{}}
	Division of Nuclear Physics, Pittsburgh/Carnegie Mellon University \newline Talk: \textsc{CUORE and Background Reduction Case Studies for CUPID} & Oct 2017 \\
	Conference on Science at SURF, South Dakota \newline Invited talk: \textsc{Status of the CUORE $0\nu\beta\beta$ Decay Search} & May 2017 \\
	Fermilab - Frontiers of Liquid Scintillator Technology \newline Invited talk: \textsc{Particle ID and event reconstruction algorithms in scintillator} & Mar 2016 \\
	DOE project review, Honolulu, Hawaii \newline Talk: \textsc{High Energy Analysis and Application to Dark Matter Search in KamLAND} & Jul 2015 \\
	Neutrino, Kyoto, Japan \newline Poster: \textsc{Indirect Dark-Matter Detection Through KamLAND} & Jun 2012 \\
	University of Hawaii Campus Open-house \newline Talks: \textsc{What is a Neutrino?}, \textsc{mini-TimeCube: The World's Smallest Neutrino Detector} & Nov 2010, 2011 \\
	Applied Antineutrino Physics, Sendai, Japan \newline Talk: \textsc{mini-TimeCube: A Portable Directional Neutrino Detector} & Aug 2010 \\
	DOE project review, Honolulu, Hawaii \newline Talk: \textsc{KamLAND Summary} & Sep 2009 \\
	Fermilab - International Neutrino Summer School \newline Talk: \textsc{Student presentation: How to solve $\theta_{23}$ degeneracy} & Jul 2009 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\clearpage
\renewcommand\refname{Publications} %changes default name to Publications

\nocite{*} %lists everything in the .bib file
%\bibliographystyle{plain} %hundreds of styles to choose from
%\bibliography{publications.bib} %name of your .bib file
%\newrefcontext[sorting=nty]
%\printbibliography[title=Alphabetic]
\bibliographystyle{habbrvyr}
\bibliography{publications.bib} %name of your .bib file


%\section{Publications}
%
%\noindent\begin{tabular}{rp{11cm}}
%	\multicolumn{2}{l}{\textsc{mini-TimeCube}} \\
%	2015 (expected) & V.A. Li et al., \textsc{mini-TimeCube}, RSI Invited Review\\
%	\multicolumn{2}{c}{} \\
%	\multicolumn{2}{l}{\textsc{KamLAND}} \\
%	2015 (expected) & K. Asakura et al., \textsc{Search for the Proton Decay
%Mode $p \rightarrow \overline{\nu} K^{+}$ with KamLAND}, Phys. Rev. D\\
%	Mar. 2015 & K. Asakura et al., \textsc{Study of electron anti-neutrinos
%	associated with gamma-ray bursts using KamLAND}, arXiv:1503.02137v1\\
%	Feb. 2015 & T.I. Banks et al., \textsc{A compact ultra-clean system for
%	deploying radioactive sources inside the KamLAND detector},
%	10.1016/j.nima.2014.09.068\\
%	Jan. 2015 & C. Lane et al., \textsc{A new type of Neutrino Detector for
%	Sterile Neutrino Search at Nuclear Reactors and Nuclear Nonproliferation
%	Applications}, arXiv:1501.06935v1\\
%	May 2014 & A. Gando et al., \textsc{7Be Solar Neutrino Measurement with
%	KamLAND}, arXiv:1405.6190v1\\
%	Aug. 2011 & S. Abe et al., \textsc{Measurement of the 8B Solar Neutrino
%	Flux with the KamLAND Liquid Scintillator Detector},
%	10.1103/PhysRevC.84.035804\\
%	Aug. 2011 & J. Kumar, J.G. Learned, M. Sakai, S. Smith,
%	\textsc{Dark Matter Detection With Electron Neutrinos in Liquid
%	Scintillation Detectors}, Phys. Rev. D84 (2011) 036007\\
%\end{tabular}

%----------------------------------------------------------------------------------------
%   STATEMENT OF TEACHING PHILOSOPHY AND EXPERIENCE
%----------------------------------------------------------------------------------------

\clearpage
\section{Statement of Teaching Philosophy and Experience}

Throughout my academic career, I have been heavily involved in teaching and
mentoring students from a wide range of cultures and backgrounds. This has
included working as a teaching assistant during my graduate studies at
University of Hawaii at Manoa where I organized and led 2 undergraduate Physics
Laboratory classes of over 20 students each for a total of 3 semesters. In
addition, I have also led weekly, 2 hour long, one-on-one tutoring sessions for
3 semesters. The ethnic and cultural atmosphere in Hawaii is one of the most
diverse on the planet. The University of Hawaii system not only attracts
students internationally from Asia and from around the globe, but also serves
as the hub of higher learning for students coming from countries in the Pacific
Rim such as the Marshall Islands and Micronesia. In this cultural melting pot,
instructors are required to effectively convey information in an inclusive and
efficient way while understanding each of the students' cultures and needs as
best as possible. For example, these needs may include supplemental instruction
if English is not the student's primary language, or additional attention if
the student comes from a background where little emphasis is placed on STEM
fields. Student evaluations for the effectiveness of my teaching and ability to
communicate were ``excellent''.

My philosophy for teaching undergraduate Physics is to never get bogged down by
the theory or equations. The primary driving force of a person's ability to
learn is one's own self motivated curiosity. No other incentive to learn is
more powerful and longer lasting than this. Therefore an instructor's priority
at the undergraduate level should be focused on encouraging and cultivating the
student's interest and curiosity. When I begin a class or introduce a new
concept to students, I never begin with equations. I always first show them the
experiment itself or introduce the context in an illustrative way. This is to
engage the students' interest and entice their curiosity before going into
anything that may slow them down and deter their motivation. Curiosity is where
science is born from and curiosity is what drives science forward. This is true
whether one is an undergraduate student or a Nobel laureate.

In society today, there is an unfortunate misconception that Physics is a
difficult subject and that it is only for \textit{smart} students. Nothing
could be further from the truth. When students feel that they are not good
enough or smart enough to follow the class, it is important to let them know
that Physics is not about intelligence, but about curiosity driven diligence
and hard work. All professional Physicists today stand on the shoulders of the
giants of the past, and almost no research is done solely alone, but through
collaboration and teamwork. No one is \textit{smart} enough to do all the work
by one's self. I usually use myself as an example. I could not attend a leading
world-class research institute during my undergraduate school days, but I
believe through diligence and hard work, I have had the opportunity to work
with some of the most talented and innovative Physicists in the field.

Finally, my experience in mentoring students has also included teaching Geant4
Monte Carlo particle simulations to 3 undergraduate and 3 Ph.D. students at the
University of California, Los Angeles (UCLA). My method for teaching this
simulation coding toolkit is to learn together with the students by going into
the gritty details of the code together. This is because learning how to code
is not just about acquiring the skill to code, but about learning the culture
of coding. By this I mean that there are certain useful tools and methods of
accomplishing a task that can only be learned through going into the gritty
details and getting \textit{dirty} with someone more knowledgeable than you
instead of learning from a straightforward top-down approach. This can be
summed up in the popular saying: ``looking at someone else coding is the best
way to learn how to code''. Through this method my students have grown to
successfully been able to take on simulation tasks of their own and contribute
effectively to the collaboration.

%----------------------------------------------------------------------------------------
%	STATEMENT OF SCHOLARSHIP
%----------------------------------------------------------------------------------------

\clearpage
\section{Statement of Scholarship}

I have been involved with the CUORE (Cryogenic Underground Observatory for Rare
Events) experiment at the University of California, Los Angeles since 2016. The
main objective of the CUORE experiment is to hunt for neutrinoless double beta
($0\nu\beta\beta$) decay using \ce{^{130}Te}. My work in the collaboration
involves development of the Geant4 Monte Carlo simulation together with a
graduate student colleague to better understand the radioactive backgrounds in
the detector. The energy spectrum of the backgrounds in the so called alpha
region ($\gtrsim \SI{2.5}{\mega\electronvolt}$) exhibit peculiar features that,
if understood correctly will better explain the types of background sources and
their distributions in the various parts and materials comprising the detector.
This can help us to better understand our backgrounds and to extrapolate this
knowledge to the energy region of interest
(\SIrange{2465}{2575}{\kilo\electronvolt}) for $0\nu\beta\beta$ decay search in
\ce{^{130}Te}. I have previously also mentored 2 undergraduate students and
worked together with them to simulate and test new radioactivity shielding
schemes for further background reduction in future $0\nu\beta\beta$ decay
experiments that are to follow CUORE. The ultimate goal of this endeavor is to
enable our laboratory to become the leading experts in this field at UCLA.

In order to promote more dialogue and efficient teamwork, I have also organized
and led weekly Physics paper discussion group sessions involving both
undergraduate and graduate students in our laboratory at UCLA. These sessions
have helped us not only to know our own experiment better, but to increase our
common understanding of the overall field of experimental $0\nu\beta\beta$
decay search. Ultimately this has been invaluable for our team to increase
our teamwork and productivity, and become a valuable contributor to the CUORE
experiment. A paper for our first $0\nu\beta\beta$ analysis using CUORE data
was submitted for publication to PRL in late 2017, and is currently under
review (https://arxiv.org/abs/1710.07988).

%The focus of my work at the University of Hawaii has been in the directional
%detection of high energy neutrinos in scintillator and its application toward
%indirect dark matter searches, directional geo-neutrino measurements, and
%anti-nuclear proliferation techniques that involve locating the position of the
%neutrino source.
%My main interest has been in detector development and novel techniques to
%search for previously unexplored phase-space regions in neutrino physics. My
%main interest and past research experience has been in detector development
%and developing novel techniques to open new methods of exploration in neutrino
%physics. 

%In addition, I have also worked on 3 other projects: the
%\SI{1}{\kilo\tonne} liquid scintillator neutrino detection experiment KamLAND
%(Kamioka Liquid Scintillator Antineutrino Detector) in Kamioka, Japan, a
%portable \SI{2.2}{\liter} plastic scintillator neutrino detector called the
%mini-TimeCube, and scintillator R\&D for a future \SI{10}{\kilo\tonne}-scale
%deep-sea based neutrino detector HanoHano.
%
%My work in KamLAND has involved developing directional event reconstruction
%methods for high-energy $\gtrsim$\si{\giga\electronvolt} scale neutrinos and
%applying this to conduct an indirect dark matter search by looking at an excess
%flux of neutrinos from the core of the Sun and Earth. Studies done with Monte
%Carlo suggest that the accuracy of reconstructing the neutrino direction using
%this method is better than that of water-Cherenkov detectors by
%$\sim$\SI{10}{\degree} for this energy regime. This method was tested against
%initial events spilling into KamLAND from the T2K neutrino beam-line and the
%results were consistent with what was expected. I believe this is the first
%ever physics application of neutrino directionality in a scintillator
%experiment.

In addition, I have worked as the lead Geant4 simulation designer for the
mini-TimeCube collaboration at University of Hawaii at Manoa. mini-TimeCube is
an ambitious project to build the world's smallest portable neutrino detector.
In this project, I mentored 3 undergraduate students and worked in
collaboration with them to conduct case studies for optimizing the detector
design, test candidate neutron capture doping elements in plastic scintillator,
and simulate the response of the multi-channel-plate (MCP) PMTs deployed in the
detector. These studies were used during construction of the detector, and to
develop directional algorithms that are now being tested in analyses of
neutrons from test sources as well as neutrinos from nuclear reactors.
%I have also conducted simulation studies for cosmic-ray muons and long-lived
%cosmogenic background isotopes such as \ce{^{8}He} and \ce{^{9}Li}. These
%backgrounds are extremely difficult to tag due to their long life-time ($>
%\sim\si{\second}$ scale) and travel distances. The studies have been vital to
%the project. 
Working with the mini-TimeCube project has further involved designing and
fabricating PCB boards as well as contributing to the FPGA firmware for the
readout electronics. A paper summarizing our accomplishments was published in
2016 (V. A. Li et al. Invited Article: miniTimeCube. Rev. Sci. Instrum.,
87(2):021301, 2016, 1602.01405).

Finally, my work in scintillator R\&D for HanoHano, a proposed
\SI{10}{\kilo\tonne}-scale deep-sea based neutrino detector, involved designing
and building apparatuses using CAD for measuring light output of Linear
alkylbenzene (LAB) based liquid scintillators when put in large electric
potential gradients as well as testing their light transmissivities under
extreme temperatures and pressures such as those found in deep-sea
environments. This project included mentoring an undergraduate student on
techniques for shielding electronic apparatuses and working with another
graduate student on designing and operating the cold high pressure environment
device.

%As an assistant professor, I am looking for an integrated work environment
%where I can get hands-on experience together with students with detector
%hardware, electronics, and firmware development while, at the same time,
%applying my skills in simulation and analysis.

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\clearpage
\section{References}

\noindent\begin{tabular}{rp{12cm}}
\multicolumn{2}{l}{\footnotesize{Supplied upon request or please contact in
	person.}}\\
\multicolumn{2}{c}{}\\
Huan H. \textsc{Huang} & Professor, University of California, Los Angeles, +1-310-825-9297\\
& \href{mailto:huang@physics.ucla.edu}{\nolinkurl{huang@physics.ucla.edu}}\\
John G. \textsc{Learned} & Professor, University of Hawaii at Manoa, +1-808-956-2964\\
& \href{mailto:jgl@phys.hawaii.edu}{\nolinkurl{jgl@phys.hawaii.edu}}\\
Yury \textsc{Kolomensky} & Professor, University of California, Berkeley, +1-510-642-9619\\
& \href{mailto:ygkolomensky@lbl.gov}{\nolinkurl{ygkolomensky@lbl.gov}}\\
Brian K. \textsc{Fujikawa} & Staff Scientist, Lawrence Berkeley National Laboratory, +1-510-486-4398\\
& \href{mailto:bkfujikawa@lbl.gov}{\nolinkurl{bkfujikawa@lbl.gov}}\\
Lindley \textsc{Winslow} & Jerrold R. Zacharias Assistant Professor, MIT, +1-617-253-2332\\
& \href{mailto:lwinslow@mit.edu}{\nolinkurl{lwinslow@mit.edu}}\\ 
Thomas \textsc{O'Donnell} & Assistant Professor, Virginia Tech, +1-540-231-3308\\
& \href{mailto:todonnell@vt.edu}{\nolinkurl{todonnell@vt.edu}}\\

%Kunio \textsc{Inoue} & Professor, Tohoku Univ./RCNS, +81-22-795-6727,
%\href{mailto:inoue@awa.tohoku.ac.jp}{\nolinkurl{inoue@awa.tohoku.ac.jp}}\\
%
%Jason \textsc{Kumar} & Assoc. Professor, Univ. of Hawaii at Manoa, +1-808-956-2972,
%\href{mailto:jkumar@phys.hawaii.edu}{\nolinkurl{jkumar@phys.hawaii.edu}}\\
%
%Jelena \textsc{Maricic} & Assoc. Professor, Univ. of Hawaii at Manoa, +1-808-956-7176,
%\href{mailto:jelena@phys.hawaii.edu}{\nolinkurl{jelena@phys.hawaii.edu}}\\

%Adam \textsc{Bernstein} & P.I. Applied Antineutrino Physics, LLNL,
%\href{mailto:bernstein3@llnl.gov}{\nolinkurl{bernstein3@llnl.gov}}\\
%\multicolumn{2}{l}{\footnotesize{(note: I have met Dr. Bernstein once during AAP
%2010 Sendai, so perhaps he knows me least within the listed referrers.)}}\\
\end{tabular}

%----------------------------------------------------------------------------------------

\end{document}
