%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage{fontspec}
%\setmainfont{Fontin} % Main document font
%\usepackage{fontawesome}
%\usepackage{fontspec} % For loading fonts
%\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
\setmainfont{Times New Roman} % Main document font

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{siunitx}
\DeclareSIUnit\year{yr}
\usepackage[version=4]{mhchem}
\usepackage{tabularx}
\setlength{\tabcolsep}{12pt}

\usepackage{ragged2e}

% personal data
\name{Michinari}{Sakai}
\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{1235 Solano Ave Apt 10}{Albany, CA 94706}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{808-206-4357}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{michsakai@berkeley.edu}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
%\recipient{SNOLAB}{Creighton Mine \#9\\1039 Regional Road 24\\Lively, ON P3Y 1N2\\Canada}
\recipient{Department of Physics}{University of Washington}
\date{November 27, 2019}
\opening{Dear Graduate Admissions Committee,}
%\closing{Best wishes,}
\closing{Thank you for your time,}
%\enclosure[Attached]{curriculum vit\ae{}, research statement, publication list, list of referees}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

\justifying
It is my sincere pleasure to offer my unreserved recommendation for Samuel
Naugle to your academic program. Samuel Naugle has been working closely with me
at Lawrence Berkeley National Laboratory from May 2019 on a local R\&D project
to investigate the micro-physical optical properties of wavelength shifter thin
film materials. During this time, I was able to personally witness his work
routine on a daily basis and assess his future potential as a scientist.

He is an exceptional student in his ability to quickly absorb new ideas and
skills to perform original research in a scientific laboratory setting. He was
first given the task to learn the Monte Carlo simulation code for the project
in order to study the systematic effects of the optical alignment of the
hardware setup. He mastered this quickly and was producing original work in a
very short period of time. During the past months, I have also had the opportunity
to spend many hours with him discussing new strategies to mitigate hardware
issues that arose from time to time, and I appreciate his valuable input in
leading the project to success. He has a natural ability to develop creative
new ideas toward solving complex hardware problems and I can testify that in
more than one occasion has his insight played a key role in the project. I
would also like to highlight his very high ability to work responsibly as a
team player, and maintain a professional and friendly relationship with both
his mentors as well as his peers. He has a bright and friendly personality and
is liked by all in our research group. I believe that his character will take
him far where ever people skills and team work are important. I make these
statements not as upper management, but as a colleague and mentor who has
worked with him day in and day out during the past 6 months.

I see Samuel having exceptional potential for future development as a
professional scientist and toward contributing original work to the field.
I firmly believe Samuel would be an asset to any organization, but he has
chosen your particular program as the place to develop himself further as
scientist. I am absolutely confident that his admission to your program would
be a decision you will not regret.

I would be happy to answer any questions you may have or to discuss my
recommendation in further detail. Please feel free to call me at 808-206-4357.

\makeletterclosing
\vspace{-4cm}
\normalfont{Post-doctoral researcher}\\
\normalfont{University of California, Berkeley}
\end{document}


%% end of file `template.tex'.
